%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,bitstream]{moderncv}

% possible options include font size ('10pt', '11pt' and '12pt'),
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
% 'executivepaper' and 'landscape') and font family ('sans' and
% 'roman')

%\renewcommand{\familydefault}{bitstream-charter} % to set the default font;
%use '\sfdefault' for the default sans serif font, '\rmdefault' for
%the default roman one, or any tex font name

\moderncvstyle{classic}
% style options are 'casual' (default), 'classic', 'oldstyle' and
% 'banking'

\moderncvcolor{blue}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'black'

\nopagenumbers{}

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}

\name{Harsh}{Gupta}
\address{E-210, Azad Hall of Residence}{Indian Institue of Technology}{Kharagpur - 721302 India}
\email{gupta.harsh96@gmail.com}
% \homepage{http://hargup.github.io}
\github{http://github.com/hargup/}

\newcommand{\tinygap}{\vspace{7 pt}}
\newcommand{\largegap}{\vspace{10 pt}}

\begin{document}

\makecvtitle

\largegap
\section{Education}

\tinygap
\vbox{\cventry{2012--2017}{Master of Science, Bachelor of Science}{Indian Institute of Technology Kharagpur}{}{}{
Mathematics \& Computing - \textbf{7.89/10 GPA}}}

\largegap
\section{Work Experience}

\tinygap
\cventry{June 2015-- Present}{
    Wikipedia Gender Indicators (WIGI)
}{
    Developer and Researcher
}{}{}{
%
    Developed the website for WIGI and did preliminary analytics on Field of
    Work and Occupation data of gendered biographies on Wikipedia along with a
    project mate.
%
}


\tinygap
\cventry{May 2015--July 2015}{
    Continuum Analytics
}{
    Software Engineering Intern
}{}{}{
%
    Automated the process of building noarch conda packages from Python
    Packaging Index (PyPI).
    Added support for numpy.median in Numba, a NumPy aware optimizing compiler
    for Python.
%
}


\tinygap
\cventry{June 2015--Sept 2015}{
    SymPy
}{
  Google Summer of Code Mentor
}{}{}{
%
    Guided a Google Summer of Code student in improving the new symbolic
    solvers in SymPy.
%
}


\tinygap
\cventry{Dec 2014--Jan 2015}{
    Afra: Genome Annotation for the Masses
}{
  Software Engineering Intern
}{}{}{
%
    Wrote a test suit for annotation editing functionality on the jasmine framework in JavaScript.
    Wrote a ruby script to export submission to GFF3 format.
%
}


\tinygap
\cventry{Sept 2013--Present}{
    SymPy
}{
  Open Source Contributor
}{}{}{
%
    Fixed the evaluation of ImageSet for intervals, wrote an inequality solver,
    added as\_set method for bool and relationals and wrote a Set Difference
    class.
%
}

\tinygap
\cventry{May 2014--Sept 2014}{
  SymPy
}{
  Google Summer of Code Student
}{}{}{
%
    Rewrote symbolic solvers for Algebraic equations. The new solvers provides
    a clear input and output interface, removes inconsistency between real and
    complex solvers and supports infinite solutions.
%
}

\tinygap
\cventry{Oct 2013-- Sep 2014}{
    AGV IIT KGP: Autonomous Ground Vehicle
}{
  Team Member
}{}{}{
%
    Implemented basic motion planning algorithms and basic computer
    vision system.
    AGV IIT KGP is a research group at IIT Kharagpur which
    participated in Intelligent Ground Vehicle Competition(IGVC) 2014 held at
    Michigan.
%
}


\tinygap
\cventry{May 2013-- July 2013}{
  Breathe Arts
}{
  Web Developement Intern
}{}{}{
%
    Implemented a login system using OpenID and fixed the password recovery system
    on Breathe Art's ASP.NET online art galleries.
%
}

% \largegap
% \section{Skills \& Expertise}
%
% \cventry{}{Competent\hspace{0.1cm}}{Python}{}{}{}
% \cventry{}{Proficient\hspace{0.4cm}}{C, Git, Vim, JavaScript}{}{}{}
% \cventry{}{Familiar\hspace{0.7cm}}{C++, MIT Scheme, HTML, CSS, Java, Ruby, \LaTeX}{}{}{}


% \largegap
% \section{Course Work}
%
% \tinygap
% \vbox{\cventry{}{Mathematics}{Modern Algebra, Linear Algebra, Transform
% Calculus, Discrete Mathematics, Real Analysis, Numerical Solution to Ordinary
% and Partial Differential Equations, Partial Differential Equations, Probability
% and Statistics}{}{}{}}
% \vbox{\cventry{}{Computer Science}{Programming and Data Structures, Design and
% Analysis of Algorithms, Computer Organisation and Architecture, Object
% Oriented System Design}{}{}{}}

\end{document}
